A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-07-03 docs/methods/erosion_methods.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation}
\label{s:formulation}
We start by defining the main variables used to model erosion.  We consider flows that are confined by a solid wall $\Gamma$ that encloses $M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.  The bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.  Therefore, the boundary of the fluid domain is $\bd\Omega = \Gamma \cup \gamma$. On each body, $\nn$ and $\ss$ denote the unit normal and unit tangent vectors respectively.  Throughout the paper, we adopt the convention that $\ss$ points in the counterclockwise direction and $\nn$ points out of the fluid domain (i.e.~into the bodies). Neglecting inertial forces, the dynamics of the fluid is fully determined by the position of the bodies $\xx_\ell(s,t) \in \gamma_\ell$, where $s$ is the arclength and $t$ is time.  Given $\xx_\ell(s,t)$, $\ell=1,\ldots,M$, derived variables include the fluid velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the bounding wall, we prescribe a velocity $\UU(\xx,t)$.  Then, the governing equations are
\begin{equation}
\label{eqn:erosionModel}
\begin{split}
  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{conservation
of momentum}\\
\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
bodies} \\
\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
velocity} \\
\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
&&\mbox{\em erosion model} .
\end{split}
\end{equation}
where $\Vn$ is the normal velocity of the interface. Parameters include the fluid viscosity $\mu$ and the material-dependent erosion constant $\CE$, as well as a characteristic flow speed $U^*$ and domain scale $L^*$. Non-dimensionalization, however, allows us to remove these parameters from consideration. We non-dimensionalize the Stokes equations in the standard way, equivalent to setting $\mu = 1$ above. For interface evolution, we scale time on the so-called erosion timescale $T^* = {L^*}^2/(\CE \mu U)$, which can be achieved by simply setting $\CE = 1$ above. For the sake of numerical stability, we will modify the erosion model in Section~\ref{sec:thetaL}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation}
\label{s:formulation}
We start by defining the main variables used to model erosion.  We consider flows that are confined by a solid wall $\Gamma$ that encloses $M$ eroding bodies as diagrammed in Fig.~\ref{fig:schematic}.  The bodies are denoted as $\gamma_\ell$, $\ell=1,\ldots,M$, and we write $\gamma = \gamma_1 \cup \cdots \cup \gamma_M$.  Therefore, the boundary of the fluid domain is $\bd\Omega = \Gamma \cup \gamma$. On each body, $\nn$ and $\ss$ denote the unit normal and unit tangent vectors respectively.  Throughout the paper, we adopt the convention that $\ss$ points in the counterclockwise direction and $\nn$ points out of the fluid domain (i.e.~into the bodies). Neglecting inertial forces, the dynamics of the fluid is fully determined by the position of the bodies $\xx_\ell(s,t) \in \gamma_\ell$, where $s$ is the arclength and $t$ is time.  Given $\xx_\ell(s,t)$, $\ell=1,\ldots,M$, derived variables include the fluid velocity $\uu$, the pressure $p$, and the shear stress $\tau$.   On the bounding wall, we prescribe a velocity $\UU(\xx,t)$.  Then, the governing equations are
\begin{equation}
\label{eqn:erosionModel}
\begin{split}
  \mu \Delta \uu = \grad p, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{conservation
of momentum}\\
\grad \cdot \uu = 0, &\hspace{20pt} \xx \in \Omega, \gap &&\mbox{\em conservation of mass} \\
\uu = 0, &\hspace{20pt} \xx \in \gamma, \gap &&\mbox{\em no slip on the
bodies} \\
\uu = \UU, &\hspace{20pt} \xx \in \Gamma, \gap &&\mbox{\em outer wall
velocity} \\
\Vn = \CE \, \abs{\tau}, &\hspace{20pt} \xx \in \gamma,
&&\mbox{\em erosion model} .
\end{split}
\end{equation}
where $\Vn$ is the normal velocity of the interface. Parameters include the fluid viscosity $\mu$ and the material-dependent erosion constant $\CE$, as well as a characteristic flow speed $U^*$ and domain scale $L^*$. Non-dimensionalization, however, allows us to remove these parameters from consideration. We non-dimensionalize the Stokes equations in the standard way, equivalent to setting $\mu = 1$ above. For interface evolution, we scale time on the so-called erosion timescale $T^* = {L^*}^2/(\CE \mu U^*)$, which can be achieved by simply setting $\CE = 1$ above. In Section~\ref{sec:thetaL}, we will make slight modifications to the erosion model for better numerical stability.
